### 2009-07-09 docs/architecture/architecture.tex
more intro + fix sectioning

\section{MAESTRO Architecture}

\subsection{MAESTRO Directory Structure}

@@

\subsection{BoxLib Data Structures}

\subsubsection{\boxtype}

@@

\subsubsection{\fab}

@@

\subsubsection{\multifab}

@@

\subsubsection{\boxarray}

@@

\subsubsection{\mlboxarray}

@@

\subsubsection{\mllayout}

\subsubsection{\bctower}

\subsection{Example: Accessing State Data}

@@

\subsection{Working with Multifabs}

\subsection{Filling Ghostcells}

\subsection{Boundary Conditions}

>>>>

\section{MAESTRO Directory Structure}

@@

\section{BoxLib Data Structures}

MAESTRO's gridding is handled by the boxlib library.  The underlying
idea in boxlib is to allow for adaptive mesh refinement.  The domain
is broken into boxes.  At the coarsest (base) level of refinement, the
entire computational domain is covered, either by one box or broken
across many boxes.  Higher levels of refinement have finer zones
(typically $2\times$).  Only a portion of the domain may be covered by
the higher levels of refinement.  \MarginPar{Nesting?}
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).

To simplify the description of the underlying AMR grid, boxlib
provides a number of Fortran types.  We briefly summarize the major
data types below.

\subsection{\boxtype}

@@

\subsection{\fab}

@@

\subsection{\multifab}

@@

\subsection{\boxarray}

@@

\subsection{\mlboxarray}

@@

\subsection{\mllayout}

\subsection{\bctower}

\section{Example: Accessing State Data}

@@

\section{Working with Multifabs}

\section{Filling Ghostcells}

\section{Boundary Conditions}
